---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

omdbapi is an R package wrapper for the [Open Movie Database API](http://www.omdbapi.com/)

The following functions are implemented:

- `find_by_id`:	Retrieve OMDB info by IMDB ID search
- `find_by_title`:	Retrieve OMDB info by title search
- `print.omdb`:	Print an omdb result
- `search_by_title`:	Lightweight omdb title search

### News

- Version `0.1.0.9000` released

### Installation

```{r installation, eval=FALSE}
devtools::install_github("hrbrmstr/omdbapi")
```

```{r setwidth, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=80)
```

### Usage

```{r usage}
library(omdbapi)

# current verison
packageVersion("omdbapi")

search_by_title("Captain America")

search_by_title("Captain America", year_of_release=2013)

games <- search_by_title("Captain America", type="game")
print(games)

find_by_title(games$Title[1])

find_by_title("Game of Thrones", type="series", season=1, episode=1)
```

### Test Results

```{r test}
library(omdbapi)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
