---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  fig.retina = 2,
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

omdbapi is an R package wrapper for the [Open Movie Database API](https://www.omdbapi.com/)

NOTE: THE OMDB API NOW REQUIRES AN API KEY <https://www.patreon.com/posts/api-is-going-10743518>

The following functions are implemented:

- `find_by_id`:	Retrieve OMDB info by IMDB ID search
- `find_by_title`:	Retrieve OMDB info by title search
- `get_actors`:	Get actors from an omdb object as a vector
- `get_countries`:	Get countries from an omdb object as a vector
- `get_directors`:	Get directors from an omdb object as a vector
- `get_genres`:	Get genres from an omdb object as a vector
- `get_writers`:	Get writers from an omdb object as a vector
- `search_by_title`:	Lightweight OMDB title search

### News

- Version `0.3.0` released (API key support & https URL switch)
- ibartomeus adds pagination option.
- Version `0.1.0.9000` released
- Version `0.2.0.9000` released - better types in the data frames and `get_` methods to split the fields with multiple entries

### Installation

```{r installation, eval=FALSE}
devtools::install_github("hrbrmstr/omdbapi")
```

```{r setwidth, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=80)
```

### Usage

```{r usage}
library(omdbapi)
library(tidyverse)

# current verison
packageVersion("omdbapi")

search_by_title("Captain America")

search_by_title("Star Wars", page = 2)

search_by_title("Captain America", year_of_release=2013)

games <- search_by_title("Captain America", type="game")
glimpse(games)

find_by_title(games$Title[1])

find_by_title("Game of Thrones", type="series", season=1, episode=1)

get_genres(find_by_title("Star Trek: Deep Space Nine", season=5, episode=7))

get_writers(find_by_title("Star Trek: Deep Space Nine", season=4, episode=6))

get_directors(find_by_id("tt1371111"))

get_countries(find_by_title("The Blind Swordsman: Zatoichi"))
```

```{r cache=TRUE}
ichi <- search_by_title("Zatoichi")
pb <- progress_estimated(length(ichi$imdbID))
zato <- purrr::map_df(ichi$imdbID, find_by_id)

zato
```

```{r fig.width=10, fig.height=2.5}
ggplot(zato, aes(x="IMDB Rating", imdbRating)) + 
  geom_boxplot() +
  scale_y_continuous(limits=c(0,10)) +
  coord_flip() +
  labs(x=NULL, y=NULL, title="Distribution of IMDB Ratings for Zatoichi movies") +
  hrbrthemes::theme_ipsum_rc(grid="X")
```

### Test Results

```{r test}
library(omdbapi)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
