---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

omdbapi is an R package wrapper for the [Open Movie Database API](http://www.omdbapi.com/)

The following functions are implemented:

- `find_by_id`:	Retrieve OMDB info by IMDB ID search
- `find_by_title`:	Retrieve OMDB info by title search
- `get_tv_data`:	Retrieve IMDB ratings for all episodes of a TV series
- `get_actors`:	Get actors from an omdb object as a vector
- `get_countries`:	Get countries from an omdb object as a vector
- `get_directors`:	Get directors from an omdb object as a vector
- `get_genres`:	Get genres from an omdb object as a vector
- `get_writers`:	Get writers from an omdb object as a vector
- `print.omdb`:	Print an omdb result
- `search_by_title`:	Lightweight omdb title search

### News

- ibartomeus adds pagination option.
- Version `0.1.0.9000` released
- Version `0.2.0.9000` released - better types in the data frames and `get_` methods to split the fields with multiple entries
- Stan125 adds function to obtain IMDB ratings for a TV series

### Installation

```{r installation, eval=FALSE}
devtools::install_github("hrbrmstr/omdbapi")
```

```{r setwidth, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=80)
```

### Usage

```{r usage}
library(omdbapi)
library(dplyr)
library(pbapply)

# current verison
packageVersion("omdbapi")

search_by_title("Captain America")

search_by_title("Captain America", page = 2)

search_by_title("Captain America", year_of_release=2013)

games <- search_by_title("Captain America", type="game")
glimpse(games)

find_by_title(games$Title[1])

find_by_title("Game of Thrones", type="series", season=1, episode=1)

get_tv_data("True Detective")

get_genres(find_by_title("Star Trek: Deep Space Nine", season=5, episode=7))

get_writers(find_by_title("Star Trek: Deep Space Nine", season=4, episode=6))

get_directors(find_by_id("tt1371111"))

get_countries(find_by_title("The Blind Swordsman: Zatoichi"))

ichi <- search_by_title("Zatoichi")
bind_rows(lapply(ichi$imdbID, function(x) {
  find_by_id(x, include_tomatoes = TRUE)
})) -> zato

par(mfrow=c(3,1)) 
boxplot(zato$tomatoUserMeter, horizontal=TRUE, main="Tomato User Meter", ylim=c(0, 100))
boxplot(zato$imdbRating, horizontal=TRUE, main="IMDB Rating", ylim=c(0, 10))
boxplot(zato$tomatoUserRating, horizontal=TRUE, main="Tomato User Rating", ylim=c(0, 5))
par(mfrow=c(1,1))

```

### Test Results

```{r test}
library(omdbapi)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
